---
title: "Importing Columns with Percentage Values"
author: "Nozimjon Ortikov"
date: today
categories: [post]
execute: 
  warning: false
---

## **R notebook: Importing columns with percentage values**

### Libraries

```{r}
library(readxl)
library(scales)
library(tidyverse)
```

## **Reading the Data as It Is**

```{r}
data_as_it <- read_excel(path = here::here("data", 
                                     "graphs_housing_prices_data.xlsx"), 
                         skip = 1) %>% 
  rename(date ="Сана",
         growth_rate = "Ўзгариш, й/й")

data_as_it
```

In the output above, you can see that the values in the "growth_rate" column are imported as decimals rather than percentages. In some cases, it may be necessary to work with a column that displays these values as percentages.

## **Importing Columns with Percentage Values**

To convert the decimal values into percentage format, we can modify our data import process. Let’s see how to do this.

```{r}
data_with_percent <- read_excel(path = here::here("data", 
                                     "graphs_housing_prices_data.xlsx"), 
                         skip = 1) %>% 
  rename(date ="Сана",
         growth_rate = "Ўзгариш, й/й") %>% 
  mutate(growth_rate_percent = percent(growth_rate))


data_with_percent
```

Now, the `growth_rate_percent` column contains the percentage values derived from the original decimal data. This allows for **easier interpretation** and **visualization of growth rates**.
